### 2022-10-03 chapters/programming_languages/rpc/rpc.tex
add : conclusion to webframeworks section

\subsubsection{Research Questions}
In this section, we first explore the ease of implementation of this protocol, and then we will try to answer the following research questions:
\begin{description}
    \item[\textsc{RQ}~2:] How do RPC implementations consume energy regarding the number of concurrent clients?
    \item[\textsc{RQ}~1:] How do RPC implementations consume energy concerning the size of the incoming request?
\end{description}

>>>>

\subsubsection{Research Questions}
In this section, we first explore the ease of implementation of this protocol, and then we will try to answer the following research questions:
\begin{description}
    \item[\textsc{RQ}~1:] How do RPC implementations consume energy regarding the number of concurrent clients?
    \item[\textsc{RQ}~2:] How do RPC implementations consume energy concerning the size of the incoming request?
\end{description}
